Check experimental design

### 2023-05-15 analysis/01_experimental-design.Rmd
More flat multinomial logit code, as well as plots of main effects for flat and multilevel models

>>>>

# Aggregate-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions. Here we do it by aggregating up the interaction terms.

```{r aggregate-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown
# issue1 = emergency
# issue2 = environment
# issue3 = human rights
# issue4 = refugee
# transp1 = not transparent
# transp2 = transparent
# account1 = not accountable
# account2 = accountable
# fund1 = smalldonors
# fund2 = wealthydonors
# fund3 = gov grants
#

# Build out all the necessary interactions...
# ...by multiplying together the needed index-coded levels.
# Sticking exactly to the hypotheses
interactions_exact <- interactions %>% 
  as_tibble() %>% 
  rowwise() %>% 
  mutate(
    # Main Effects
    h1_high = sum(org3, org4), # oxfam and red cross
    h1_low = sum(org1, org2), # amnesty and greenpeace
    h2a_high = sum(gov_rel2,gov_rel3), # criticized and crackdown
    h2a_low = gov_rel1, # friendly
    h3a_high = sum(issue1, issue4), # emergency and refugee
    h3a_low = sum(issue2, issue3), # environment and human rights
    h4a_high = fund1, # small donors
    h4a_low = sum(fund2, fund3), # wealthy donors and gov grants
    h5a_high = transp2, # transparent
    h5a_low = transp1, # not transparent
    # First Order Interactions
    h2b_high = h1_high*h2a_high, #  oxfam and red cross * criticized and crackdown
    h2b_low = h1_low*gov_rel3, # amnesty and greenpeace * criticized
    h3b_high = h2a_high*h3a_high, # criticized and crackdown * emergency and refugee
    h3b_low = h2a_high*h3a_low, # criticized and crackdown * environment and human rights
    h4b_high = gov_rel3*fund1, # crackdown * small donors
    h4b_low = sum(gov_rel1, gov_rel2)*h4a_high, # not crackdown * not small donors
    h5b_high = h2a_high*h5a_high, # criticized and crackdown * transparent
    h5b_low = h5a_low + h2a_low*h5a_high, # not transparent + friendly * transparent + 
    # Second Order Interactions
    h4c_high = gov_rel3*h4a_high*h3a_high, # crackdown * small donors * emergency and refugee
    h4c_low = ifelse(h4c_high==1, 0, 1), # everything else
    h5c_high = h2a_high*h5a_high*h4a_high, # criticized and crackdown * transparent * small donors
    h5c_low = ifelse(h5c_high==1, 0, 1), # everything else
    h5d_high = h2a_high*h5a_high*h3a_high, # criticized and crackdown * transparent * emergency and refugee
    h5d_low = ifelse(h5d_high==1, 0, 1), # everything else
    # Third Order Interaction
    h5e_high = h2a_high*h5a_high*h3a_high*h4a_high, # criticized and crackdown * transparent * emergency and refugee * small donors
    h5e_low = ifelse(h5e_high==1, 0, 1)) %>% 
  ungroup()
# interactions <- interactions %>% 
#   as_tibble() %>% 
#   mutate(
#     # Hypothesis 3b.
#     environment_criticized = issue2 * gov_rel2,
#     humanrights_criticized = issue3 * gov_rel2,
#     refugees_criticized = issue4 * gov_rel2,
#     environment_crackdown = issue2 * gov_rel3,
#     humanrights_crackdown = issue3 * gov_rel3,
#     refugees_crackdown = issue4 * gov_rel3,
#   )

# Save interact-coded design output
# write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
write.csv(interactions_exact, here("data", "derived_data", "aggregate_interactions_exact.csv"))
```
